Prestige as a Driving Force in Cultural Transmission

### 2022-04-03 ms/PrestigeBias.tex
update

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_mutation.pdf}
  \caption{
  \textbf{Robustness of DM approximations to inclusion of mutation.} Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high mutation rate. Markers for average across simulations, error bars for 95\% confidence intervals.
  % and are condensed (+- 0.01 probability and +-40 generations) % what does that mean?
  5,000 simulations per data point; population size, $N=1000$; bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; $J\sim N(1,x^2)$ where $x$ is the mutation scale in the x-axis. % not clear enough.
  }	
  % TODO
  % see comments in previous figure
  % maybe 50% CI looks better? the bars are too large to understand. maybe a wider y range? say from 0 to 0.02?
  \label{fig:hetro_mutation}
\end{figure}

% TODO I suggest you incorporate this text to the figure caption and then we can just replace this with a sentence about how well the approximation is robust to assumptions with reference to figure.
In \cref{fig:hetro_mutation} we see the comparison when heterogeneous mutation is applied to both models. When mutation is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
We can see that even when the standard deviation is $0.1$, the metrics of both models are both similar, and close to the Kimura approximation (more details in the next section).

@@

% TODO I suggest you incorporate this text to the figure caption and then we can just replace this with a sentence about how well the approximation is robust to assumptions with reference to figure.
In \cref{fig:hetro_alpha} we relaxed our assumption of a homogeneous $\alpha$, and used a heterogeneous $\alpha$ instead. Similar to the mutation comparison, we drew $\alpha_j$ for each role-model $j$ from a normal distribution with varying scale. We again see that the metrics of both models are similar in the entire spectrum of our x-axis, and the Kimura approximation is within both confidence intervals.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Fixation probability and time}
% I think this subsection should come before the numerical validation (prev subsection) because the numerical validation also presents Kimura's equation

After finding that the DM distribution is a good approximation of the role-model choice process we turn our attention to the evolutionary dynamics.
We focus on the effect of the bias weight ($\alpha$), which determines the relative effects of success and influence on prestige bias, on the fixation probability and fixation time of an advantageous phenotype, similar to analyses in population-genetic models. % References: 
% Kimura, M. On the probability of fixation of mutant genes in a population. Genetics 47, 713–9 (1962).
% Kimura, M. & Ohta, T. The Average Number of Generations until Fixation of a Mutant Gene in a Finite Population. Genetics 61, 763–71 (1969).
% Otto, S. P. & Whitlock, M. C. Fixation Probabilities and Times. in eLS (John Wiley & Sons, Ltd, 2013). doi:10.1002/9780470015902.a0005464.pub3.
For simplicity, we do not include mutation in this analysis.
As shown above, transmission in our model is approximately DM distributed with a parameters % TODO fill here from corollary 3 and eq 19, right?
% $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$. % what's \vec{V} here?
\\

>>>>

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_mutation.pdf}
  \caption{
  \textbf{Robustness of DM approximations to inclusion of estimation error.} Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high estimation error rate. Markers for average across simulations, error bars for 95\% confidence intervals.
  % and are condensed (+- 0.01 probability and +-40 generations) % what does that mean?
  5,000 simulations per data point; population size, $N=1000$; bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; $J\sim N(1,x^2)$ where $x$ is the estimation error scale in the x-axis. % not clear enough.
  }	
  % TODO
  % see comments in previous figure
  % maybe 50% CI looks better? the bars are too large to understand. maybe a wider y range? say from 0 to 0.02?
  \label{fig:hetro_error}
\end{figure}

% TODO I suggest you incorporate this text to the figure caption and then we can just replace this with a sentence about how well the approximation is robust to assumptions with reference to figure.
In \cref{fig:hetro_error} we see the comparison when heterogeneous estimation error is applied to both models. When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
We can see that even when the standard deviation is $0.1$, the metrics of both models are both similar, and close to the Kimura approximation (more details in the next section).

@@

% TODO I suggest you incorporate this text to the figure caption and then we can just replace this with a sentence about how well the approximation is robust to assumptions with reference to figure.
In \cref{fig:hetro_alpha} we relaxed our assumption of a homogeneous $\alpha$, and used a heterogeneous $\alpha$ instead. Similar to the estimation error comparison, we drew $\alpha_j$ for each role-model $j$ from a normal distribution with varying scale. We again see that the metrics of both models are similar in the entire spectrum of our x-axis, and the Kimura approximation is within both confidence intervals.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Fixation probability and time}

After finding that the DM distribution is a good approximation of the role-model choice process we turn our attention to the evolutionary dynamics.
We focus on the effect of the bias weight ($\alpha$), which determines the relative effects of success and influence on prestige bias, on the fixation probability and fixation time of an advantageous phenotype, similar to analyses in population-genetic models. % References: 
% Kimura, M. On the probability of fixation of mutant genes in a population. Genetics 47, 713–9 (1962).
% Kimura, M. & Ohta, T. The Average Number of Generations until Fixation of a Mutant Gene in a Finite Population. Genetics 61, 763–71 (1969).
% Otto, S. P. & Whitlock, M. C. Fixation Probabilities and Times. in eLS (John Wiley & Sons, Ltd, 2013). doi:10.1002/9780470015902.a0005464.pub3.
For simplicity, we do not include estimation error in this analysis.
As shown above, transmission in our model is approximately DM distributed with a parameters % TODO fill here from corollary 3 and eq 19, right?
% $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$. % what's \vec{V} here?
\\
